Automated Verification and Synthesis of Cyber-Physical Systems: Advances and Challenges

### 2018-03-12 paper.tex
fixed references
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\textcolor{blue}{Another feasible alternative to prove properties in BMC is to compute Craig interpolants for inconsistent pairs (or more generally, sets) of formulae~\cite{McMillan03,McMillan05,McMillan06,McMillan07}. This alternative approach exploits the SAT/SMT solvers' ability to produce refutations, {\it i.e.}, proofs regarding the nonexistence of counterexamples of depth less than or equal to $k$. Those proofs do not ensure whether a given property holds in the model, but they contain information about reachable states of a model.}

@@

\textcolor{blue}{Suppose that we use an SMT solver to prove that the $A \wedge B$ is unsatisfiable, {\it i.e.}, we use an SMT solver to conclude that there is no satisfying assignment to $A \wedge B$.\footnote{Note that if at any stage we can satisfy the property $\phi$ within $k$ steps from the initial state, then we have found a counterexample.} The internal steps performed by SMT solvers for reaching this conclusion can be used to construct a proof of unsatisfiability $\Pi$, from which we can derive an interpolant $F$ for the pair of formulae $\left(A,B\right)$, i.e., $F = interpolant\left(\Pi, A, B\right)$. According to Definition~\ref{interpolants}, $A$ must imply $F$ and since we defined $A$ to be the set of initial states and the first instance of $R$ (i.e., from Figure~\ref{figure:computing-image-by-interpolation}, $A=s_{0} \wedge s_{1}$), it follows that $F$ is \textit{true} in every state reachable from the initial state in one step. In other words, we can say that $F$ is an over-approximation of the forward image of $I$~\cite{McMillan03,McMillan05}. Also according to Definition~\ref{interpolants}, the formula $F \wedge B$ must be unsatisfiable (from Figure~\ref{figure:computing-image-by-interpolation}, $B=s_{2} \wedge s_{3} \wedge \ldots \wedge s_{k}$), which means that there is no state satisfying $F$ that can reach a final state $s_k$. After computing $F$, we then check whether $F$ implies $Q$. If $F$ implies $Q$, then no reachable state can satisfy the property $\phi$ and we can thus conclude that the property holds; however, since $F$ is an approximation, we can falsely conclude that the final state is reachable. In this case, we update $Q = F \vee Q$ and $A = F \wedge R_{0}$, increase the value of $k+1$ and check whether $A \wedge B$ is unsatisfiable. If $A \wedge B$ is satisfiable, we have found a valid counter-example (i.e., a path from the initial state to the final one); otherwise, we compute the interpolant $F = interpolant\left(\Pi, A, B\right)$ again and check whether $F$ implies $Q$. This procedure is stopped when we have found a valid counterexample or proved that the final state is not reachable (i.e., the property holds). The details of the algorithm and further information about the use of interpolants in model checking can be found in~\cite{McMillan03,McMillan05,McMillan06,McMillan07}}.

>>>>

\textcolor{blue}{Another feasible alternative to prove properties in BMC is to compute Craig interpolants for inconsistent pairs (or more generally, sets) of formulae~\cite{McMillan03,McMillan05}. This alternative approach exploits the SAT/SMT solvers' ability to produce refutations, {\it i.e.}, proofs regarding the nonexistence of counterexamples of depth less than or equal to $k$. Those proofs do not ensure whether a given property holds in the model, but they contain information about reachable states of a model.}

@@

\textcolor{blue}{Suppose that we use an SMT solver to prove that the $A \wedge B$ is unsatisfiable, {\it i.e.}, we use an SMT solver to conclude that there is no satisfying assignment to $A \wedge B$.\footnote{Note that if at any stage we can satisfy the property $\phi$ within $k$ steps from the initial state, then we have found a counterexample.} The internal steps performed by SMT solvers for reaching this conclusion can be used to construct a proof of unsatisfiability $\Pi$, from which we can derive an interpolant $F$ for the pair of formulae $\left(A,B\right)$, i.e., $F = interpolant\left(\Pi, A, B\right)$. According to Definition~\ref{interpolants}, $A$ must imply $F$ and since we defined $A$ to be the set of initial states and the first instance of $R$ (i.e., from Figure~\ref{figure:computing-image-by-interpolation}, $A=s_{0} \wedge s_{1}$), it follows that $F$ is \textit{true} in every state reachable from the initial state in one step. In other words, we can say that $F$ is an over-approximation of the forward image of $I$~\cite{McMillan03,McMillan05}. Also according to Definition~\ref{interpolants}, the formula $F \wedge B$ must be unsatisfiable (from Figure~\ref{figure:computing-image-by-interpolation}, $B=s_{2} \wedge s_{3} \wedge \ldots \wedge s_{k}$), which means that there is no state satisfying $F$ that can reach a final state $s_k$. After computing $F$, we then check whether $F$ implies $Q$. If $F$ implies $Q$, then no reachable state can satisfy the property $\phi$ and we can thus conclude that the property holds; however, since $F$ is an approximation, we can falsely conclude that the final state is reachable. In this case, we update $Q = F \vee Q$ and $A = F \wedge R_{0}$, increase the value of $k+1$ and check whether $A \wedge B$ is unsatisfiable. If $A \wedge B$ is satisfiable, we have found a valid counter-example (i.e., a path from the initial state to the final one); otherwise, we compute the interpolant $F = interpolant\left(\Pi, A, B\right)$ again and check whether $F$ implies $Q$. This procedure is stopped when we have found a valid counterexample or proved that the final state is not reachable (i.e., the property holds). The details of the algorithm and further information about the use of interpolants in model checking can be found in~\cite{McMillan03,McMillan05}}.
